Tutorial_2a

### 2024-12-09 Tutorial_2a.Rmd
update 2a

```{r load-pkg, results='hide'}
pkg <- c("cmdstanr", "standist", "tidyverse", "RColorBrewer", "patchwork", 
         "brms", "tidybayes", "bayesplot", "future", "parallel", "modelr",
         "rstan")

@@

>>>>

```{r load-pkg, results='hide'}
pkg <- c("cmdstanr", "standist", "tidyverse", "RColorBrewer", "patchwork", 
         "brms", "tidybayes", "bayesplot", "future", "parallel", "modelr",
         "rstan", "knitr")

@@

```{r}
kable(table, caption = "Point (mean) and 95% credible interval summary of estimated differences in hazard, for each time bin and contrast, in the average participant.")
```
